Verifying Interactive WebSocket Applications in TypeScript

### 2020-01-23 PLACES_2020/main.tex
PLACES: update inrtoduction

Modern interactive web applications aim to provide a highly responsive user experience by minimising the communication latency between clients and servers.
Whilst the HTTP request-response model is sufficient for retrieving static assets, applying the same stateless communication approach for interactive use cases (such as a multiplayer game) introduces undesirable performance overhead from having to frequently set up new connections for client-server interactions.
Developers have since adopted other communication transport abstractions over HTTP connections such as the WebSockets protocol \cite{WebSocketRFC} to enjoy low-latency full-duplex client-server communication in their applications over a single persistent connection.
Enabling more complex communication patterns caters for more interactive use cases (such as real-time multiplayer games), but introduces additional correctness concerns to the developer.

>>>>

Modern interactive web applications aim to provide a highly responsive user experience by minimising the communication latency between clients and servers.
Whilst the HTTP request-response model is sufficient for retrieving static assets, applying the same stateless communication approach for interactive use cases (such as real-time multiplayer games) introduces undesirable performance overhead from having to frequently set up new connections for client-server interactions.
Developers have since adopted other communication transport abstractions over HTTP connections such as the WebSockets protocol \cite{WebSocketRFC} to enjoy low-latency full-duplex client-server communication in their applications over a single persistent connection.
Enabling more complex communication patterns caters for more interactive use cases, but introduces additional correctness concerns to the developer.
